Assessment of the KLGO Coastal Waterbird Survey Monitoring Program

### 2019-05-07 analysis/paper/paper.Rmd
changed paper.Rmd chunk options / deleted old scripts.

```{r Fig-SiteAccess, echo=FALSE, eval=TRUE, cache=TRUE, fig.show= 'asis', fig.cap="",warning= FALSE}
# print(plot_access)
```

@@

```{r Fig-SurveyEffort, echo=FALSE, eval=TRUE, cache=TRUE, fig.show= 'asis', fig.cap="",warning= FALSE}
print(plot_duration)
```

@@

```{r Fig-SiteSurveyCompletion, echo=FALSE, eval=TRUE, cache=FALSE, fig.show= 'asis', fig.cap="Need to add caption.",warning=FALSE}

@@

```{r Fig-SurveyTiming1, echo=FALSE, eval=TRUE, cache=FALSE, fig.show= 'asis', fig.cap="The annual dates of the first and last survey have both varied by over a month across the years."}

@@

JOEL - I specified ncol = 3 in the facet command but my html doesn't update with it (I know the command itself works since I can see the zoom in the script)? Are you able to see it? and/or does it work in solving the space problem?
```{r Fig-SurveyTiming2, echo=FALSE, eval=TRUE, cache=FALSE, fig.show= 'asis', fig.cap=""}

@@

```{r Fig-SurveyDates2, echo=FALSE, eval=TRUE, cache=FALSE, fig.show= 'asis', fig.cap="The last sighting of each species each year.", warning=FALSE}
print(plot_timing_2)
```

@@

```{r Fig-SpeciesTiming2, echo=FALSE, eval=TRUE, cache=TRUE, fig.show= 'asis', fig.cap="For each of the target species, the dates on which they were observed in any of the sample areas."}

>>>>

```{r Fig-SiteAccess, echo=FALSE, eval=TRUE, cache=TRUE, fig.show= 'asis',fig.height=20, fig.width=12, fig.cap="",warning= FALSE}
# print(plot_access)
```

@@

```{r Fig-SurveyEffort, echo=FALSE, eval=TRUE, cache=TRUE, fig.show= 'asis', fig.height=15, fig.width=12,fig.cap="",warning= FALSE}
print(plot_duration)
```

@@

```{r Fig-SiteSurveyCompletion, echo=FALSE, eval=TRUE, cache=FALSE, fig.show= 'asis',fig.height=10, fig.width=18, fig.cap="Need to add caption.",warning=FALSE}

@@

```{r Fig-SurveyTiming1, echo=FALSE, eval=TRUE, cache=FALSE, fig.show= 'asis',fig.height=10, fig.width=12, fig.cap="The annual dates of the first and last survey have both varied by over a month across the years."}

@@

@@

```{r Fig-SurveyDates2, echo=FALSE, eval=TRUE, cache=FALSE, fig.show= 'asis', fig.height=20, fig.width=12, fig.cap="The last sighting of each species each year.", warning=FALSE}
print(plot_timing_2)
```

@@

```{r Fig-SpeciesTiming2, echo=FALSE, eval=TRUE, cache=TRUE, fig.show= 'asis', fig.height=25, fig.width=12, fig.cap="For each of the target species, the dates on which they were observed in any of the sample areas."}
